\%-------------------------
\% Resume in Latex
\% Author : Jake Gutierrez
\% Based off of: https://github.com/sb2nov/resume
\% License : MIT
\%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\%-------------------------
\% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\% Centered header: name on top, contact details below
\% Usage: \resumeHeading{Full Name}{detail1 $|$ detail2 $|$ detail3 ...}
\newcommand{\resumeHeading}[2]{\%
  \begin{center}
    {\Huge \scshape #1} \\ \vspace{1pt}
    \small #2
  \end{center}
}

\%-------------------------------------------
\%\%\%\%\%\%  RESUME STARTS HERE  \%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%


\begin{document}

\resumeHeading{BRIAN O. DIYAOLU}{(662) 867-3529 $|$ \href{mailto:briandiyaolu09@gmail.com}{briandiyaolu09@gmail.com} $|$ LinkedIn $|$ Portfolio $|$ GitHub $|$ Jackson, MS}

\section{SUMMARY OF KEY QUALIFICATIONS}
\resumeItemListStart
    \resumeItem{Epic Certified Applications Analyst with expertise in configuring enterprise scheduling systems, decision trees, and workflow automation in healthcare.}
    \resumeItem{Advanced data professional proficient in SQL, Python, R, and BI tools, converting raw data into strategic insights via dashboards and predictive modeling.}
    \resumeItem{MBA and MS in Information Systems graduate adept at aligning technical solutions with business strategy to deliver scalable and outcome-driven results.}
\resumeItemListEnd

\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading{Mississippi State University}{Starkville, MS}{M.S. in Information Systems, GPA: 3.82}{May 2025}
    \resumeSubheading{Mississippi State University}{Starkville, MS}{M.B.A., GPA: 3.82}{May 2025}
    \resumeSubheading{Mississippi Valley State University}{Itta Bena, MS}{B.S. in Computer Science, Magna Cum Laude, GPA: 3.58}{May 2023}
\resumeSubHeadingListEnd

\section{PROFESSIONAL EXPERIENCE}
\resumeSubHeadingListStart
    \resumeSubheading{Epic Applications Analyst}{July 2025 – Present}{University of Mississippi Medical Center}{Jackson, MS}
    \resumeItemListStart
        \resumeItem{Configured Epic Cadence components for 700+ providers, optimizing enterprise scheduling operations.}
        \resumeItem{Developed automated rule logic for workqueues, reducing manual tasks by [x\%] and enhancing workflow efficiency.}
        \resumeItem{Supported the Infusion Template Generator project, resolving over [x+] user issues during deployment.}
        \resumeItem{Executed Data Courier migrations with [x\%] accuracy, ensuring consistent deployment across environments.}
    \resumeItemListEnd

    \resumeSubheading{Graduate Assistant, EIS Web Development}{August 2023 – May 2025}{Mississippi State University}{Starkville, MS}
    \resumeItemListStart
        \resumeItem{Collaborated with a team to deliver web projects using agile methodology, contributing to [specific deliverable].}
        \resumeItem{Created a centralized web interface for 50+ projects, ensuring scalability for future enhancements.}
        \resumeItem{Optimized SQL queries to enhance data accuracy by 80\%, minimizing inconsistencies.}
        \resumeItem{Improved code quality and reduced production issues by 85\% through detailed testing and documentation.}
    \resumeItemListEnd

    \resumeSubheading{Consulting Analyst (MBA Capstone Project)}{January 2025 – May 2025}{Saturn Materials}{Starkville, MS}
    \resumeItemListStart
        \resumeItem{Developed a brand improvement strategy projecting [x\%] increase in visibility.}
        \resumeItem{Led data mining using Python and Google APIs, improving data quality for analysis.}
        \resumeItem{Presented actionable recommendations to enhance strategic decision-making to Saturn leadership.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{RESEARCH EXPERIENCE}
\resumeSubHeadingListStart
    \resumeSubheading{Business Forecasting Analytics Research (APEX Forecast)}{Month Year – Month Year}{}{}
    \resumeItemListStart
        \resumeItem{Designed a forecasting platform with regression models achieving 80\% prediction accuracy for financial data.}
        \resumeItem{Presented a research poster at the ADMI conference, receiving an award for innovation and projected impact.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{PROJECTS}
\resumeSubHeadingListStart
    \resumeSubheading{MBA Case Competition}{2025}{}{}
    \resumeItemListStart
        \resumeItem{Researched EV market trends for Nissan, developing a strategic roadmap under tight deadlines.}
    \resumeItemListEnd

    \resumeSubheading{Orange Telecom Case Study}{View Project}{}{}
    \resumeItemListStart
        \resumeItem{Identified key churn drivers and developed a 94\% accurate logistic regression model to predict churn, proposing strategies to improve retention by 15\%.}
    \resumeItemListEnd

    \resumeSubheading{Car Sales Analytics}{View Project}{}{}
    \resumeItemListStart
        \resumeItem{Analyzed a dataset of 500,000 vehicles, uncovering insights that informed marketing strategies.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{SKILLS \& CERTIFICATIONS}
\resumeItemListStart
    \resumeItem{Languages: Python, SQL, R, HTML, CSS}
    \resumeItem{Tools: Tableau, Power BI, Git, Wix Studio, Microsoft Office}
    \resumeItem{Certifications: Epic Cadence, Epic Decision Tree Badge, Epic Prelude, Epic Data Courier Badge}
\resumeItemListEnd

\section{ACTIVITIES \& LEADERSHIP EXPERIENCE}
\resumeItemListStart
    \resumeItem{Honors Scholar | Google Developer Club | Vice President, NSBE, MVSU Chapter}
\resumeItemListEnd

\end{document}